Annotation exploration for SCPCP000006

### 2024-10-30 analyses/cell-type-wilms-tumor-06/notebook/07_annotation_Across_Samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/07_annotation_Across_Samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

- the label transfer from the fetal kidney reference (Stewart et al.), in particular the `fetal_kidney_predicted.compartment` and `fetal_kidney:predicted.cell_type`, as well as the `mapping.score` for each compartment,

>>>>

- the label transfer from the fetal kidney reference (Stewart et al.), in particular the `fetal_kidney_predicted.compartment` and `fetal_kidney:predicted.cell_type`, as well as the `prediction.score` for each compartment,
